Marginally-Stable Thermal Equilibria of Rayleigh Benard Convection

### 2021-02-25 publication_materials/rbctest.tex
plotting tools

\usepackage{graphicx}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{enumerate}
\usepackage{varwidth}
\usepackage{{subfig}

@@

    \nabla \cdot \mathbf{u} &= 0 \label{EQ:motion1}\\
    \frac{\partial \mathbf{u}}{\partial t} + \mathbf{u} \cdot \nabla \mathbf{u} &= - \nabla p + T \hat{z} + \sqrt{\frac{Pr}{Ra}} \nabla^2 \mathbf{u} \label{EQ:motion2}\\
    \frac{\partial T}{\partial t} + \mathbf{u} \cdot \nabla T &= \frac{1}{\sqrt{RaPr}} \nabla^2 T \label{EQ:motion3}

@@

\begin{figure*}[t]
    \centering
    \subfloat{\includegraphics[width=3.4in]{flux_sup_n.png}}
    \hfill
    \subfloat{\includegraphics[width=3.4in]{EV_spectra_2ra.png}}
    \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states $Ra = 2 \times 10^5$ (top) and $Ra = 10^9$ (bottom). Advection profiles belong to marginally-stable modes. For low $Ra$ a single mode with $k_x = 1.5\pi$ is sufficient to oppose  boundary layer diffusion and facilitate heat flux throughout the bulk of the domain. For large $Ra$, high-wavenumber marginally-stable modes contribute small-scale advection profiles which tightly hug the thin boundary layers. A combination of these of profiles is necessary to transition to the $k_x = 1.5\pi$ mode.}
    \label{fig:flux}
\end{figure*}

>>>>

\usepackage{graphicx}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{enumerate}
\usepackage{varwidth}

@@

% \begin{align}
%     \nabla \cdot \mathbf{u} &= 0 \label{EQ:motion1}\\
%     \frac{\partial \mathbf{u}}{\partial t} + \mathbf{u} \cdot \nabla \mathbf{u} &= - \nabla p + T \mathhat{z} + \sqrt{\frac{Pr}{Ra}} \nabla^2 \mathbf{u} \label{EQ:motion2}\\
%     \frac{\partial T}{\partial t} + \mathbf{u} \cdot \nabla T &= \frac{1}{\sqrt{RaPr}} \nabla^2 T \label{EQ:motion3}
% \end{align}

@@

% \begin{figure*}[t]
%     \centering
%     \subfloat{\includegraphics[width=3.4in]{flux_sup_n.png}}
%     \hfill
%     \subfloat{\includegraphics[width=3.4in]{EV_spectra_2ra.png}}
%     \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states $Ra = 2 \times 10^5$ (top) and $Ra = 10^9$ (bottom). Advection profiles belong to marginally-stable modes. For low $Ra$ a single mode with $k_x = 1.5\pi$ is sufficient to oppose  boundary layer diffusion and facilitate heat flux throughout the bulk of the domain. For large $Ra$, high-wavenumber marginally-stable modes contribute small-scale advection profiles which tightly hug the thin boundary layers. A combination of these of profiles is necessary to transition to the $k_x = 1.5\pi$ mode.}
%     \label{fig:flux}
% \end{figure*}
